---
title: "Practical Machine Learning Assignment"
output: html_document
---

##Introduction
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement ??? a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

##Dataset
The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

##Loading Required Packages

```{r Loading Required Packages}
library(caret)
library(rpart)
library(rpart.plot)
library(e1071)
library(randomForest)
```

##Loading Dataset

```{r Loading Dataset}

data_training <- read.csv("pml-training.csv")
data_testing  <- read.csv("pml-testing.csv")
```

##Cleaning
Remove all columns that contains NA and remove features that are not in the testing dataset. 
The features containing NA are the variance, mean and standard devition (SD) within each window for each feature. 
Since the testing dataset has no time-dependence, these values are useless and can be disregarded. 
We will also remove the first 7 features since they are related to the time-series or are not numeric

```{r}
features <- names(data_testing[,colSums(is.na(data_testing)) == 0])[8:59]

data_training <- data_training[,c(features,"classe")]
data_testing <- data_testing[,c(features,"problem_id")]

dim(data_training)
dim(data_testing)

```

##Partitioning Data
We will split our data into a training data set(60%)and a testing data set 
```{r Partitioning Data}
set.seed(12345)
inTrain <- createDataPartition(data_training$classe, p=0.6, list=FALSE)
training <- data_training[inTrain,]
testing <- data_training[-inTrain,]
```

##Decision Tree Model
```{r Decision Tree Model}
set.seed(12345)
modFitDT <- rpart(classe ~ ., data = training, method="class")
rpart.plot(modFitDT)
```

##Prediction with Decision Tree Model
```{r Prediction Decision Tree Model}
set.seed(12345)
prediction <- predict(modFitDT, testing, type = "class")
confusionMatrix(prediction, testing$classe)
```

##Random Forest Model
```{r Random Forest Model}

modFitRF <- randomForest(classe ~ ., data = training, ntree = 1000)
```

##Prediction Random Forest Model
```{r Prediction Random Forest Model}
prediction <- predict(modFitRF, testing, type = "class")
confusionMatrix(prediction, testing$classe)
```

##Results
Since Random forest gives us 99% accuracy we use this to predict pl-testing.csv
```{r Results}
predictionRF <- predict(modFitRF, data_testing, type = "class")
predictionRF
```

